How to select predictive models for decision-making or causal inference?

### 2023-12-16 how_to_select_causal_models.tex
iter

Assumptions are necessary for causal estimands to be
identifiability
in observational settings \cite{rubin_causal_2005}. We assume the usual
strong ignorability assumptions: \emph{1)}
\emph{unconfoundedness} \mbox{$\{Y(0),
        Y(1) \} \indep A | X$}, \emph{~2)} \emph{strong overlap} ie. every patient has a
strictly positive probability to receive each treatment, \emph{3)}
\emph{consistency}, and \emph{4)} \emph{generalization} (detailed in
\ref{apd:causal_assumptions}).

>>>>

A given data needs to meet a few assumptions to enable identifying
causal estimands \cite{rubin_causal_2005}. The usual
\emph{strong ignorability} assumptions are  (details in
\ref{apd:causal_assumptions}): \emph{1)}
\emph{unconfoundedness} \mbox{$\{Y(0),
        Y(1) \} \indep A | X$}, \emph{~2)} \emph{strong overlap} ie. every patient has a
strictly positive probability to receive each treatment, \emph{3)}
\emph{consistency}, and \emph{4)} \emph{generalization}.
